### 2017-02-12 ResearchNotes/stat_exps.tex
Renamed exp 001 to stat 004, since it is a stat

@@

\subsection{\texttt{EXP\_001} - Plotting Activity of Students over the
Semester}

One plot displays the overall number of~\gls{crud} activities over the semester
and the number of \textbf{C}reate activities, \textbf{R}ead activities, etc.
Figure~\ref{fig:exp_001_all} show these plots for two courses. As it can be
seen, the number of Read activities is far greater then the others, which is to
be expected since to do any other activity, at least a Read activity has to
take place. For example, a student needs to open the Moodle page, and therefore
do a Read, to deliver a project, and therefore do a Create.

The second plot made to each course is similar, but only the Create, Update,
and Delete activities are plotted. Figure~\ref{fig:exp_001_cud} show two
examples these plots. Notice that the number of creates is not always greater
then the number of updates, and vice-versa. But the number of deletes is always
below creates and updates. This concludes that the delete activity is simply
not that common.

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/exp_001_results/fig_0_CTE-UMCED-2_all}
        \label{subfig:exp_001_0_all}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/exp_001_results/fig_3_INF7194_2_all}
        \label{subfig:exp_001_3_all}
    \end{subfigure}

    \caption
        [Exp 001 plots for all activities]
        {Exp 001 plots for all activities.}

    \label{fig:exp_001_all}
\end{figure}

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/exp_001_results/fig_0_CTE-UMCED-2_cud}
        \label{subfig:exp_001_0_cud}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/exp_001_results/fig_3_INF7194_2_cud}
        \label{subfig:exp_001_3_cud}
    \end{subfigure}

    \caption
        [Exp 001 plots for C, U, and D activities]
        {Exp 001 plots for C, U, and D activities.}

    \label{fig:exp_001_cud}
\end{figure}

>>>>

\subsection{\texttt{STAT\_004} - Plotting Activity of Students over the
Semester}

One plot displays the overall number of~\gls{crud} activities over the semester
and the number of \textbf{C}reate activities, \textbf{R}ead activities, etc.
Figure~\ref{fig:stat_004_all} show these plots for two courses. As it can be
seen, the number of Read activities is far greater then the others, which is to
be expected since to do any other activity, at least a Read activity has to
take place. For example, a student needs to open the Moodle page, and therefore
do a Read, to deliver a project, and therefore do a Create.

The second plot made to each course is similar, but only the Create, Update,
and Delete activities are plotted. Figure~\ref{fig:stat_004_cud} show two
examples these plots. Notice that the number of creates is not always greater
then the number of updates, and vice-versa. But the number of deletes is always
below creates and updates. This concludes that the delete activity is simply
not that common.

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_0_CTE-UMCED-2_all}
        \label{subfig:stat_004_0_all}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_3_INF7194_2_all}
        \label{subfig:stat_004_3_all}
    \end{subfigure}

    \caption
        [Stat 004 plots for all activities]
        {Stat 004 plots for all activities.}

    \label{fig:stat_004_all}
\end{figure}

    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_0_CTE-UMCED-2_cud}
        \label{subfig:stat_004_0_cud}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../src/stat_004_results/fig_3_INF7194_2_cud}
        \label{subfig:stat_004_3_cud}
    \end{subfigure}

    \caption
        [Stat 004 plots for C, U, and D activities]
        {Stat 004 plots for C, U, and D activities.}

    \label{fig:stat_004_cud}
\end{figure}

@@
